Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-02-26 NEUROC/manuscript-submission-version/main.tex
增加干净的提交版本

	\begin{abstract}
		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
        %
		Recently, various graph neural network libraries have emerged.
        %
        They make the development of GNNs convenient, but their performance bottlenecks on large datasets are not well studied.
        %
		In this work, we analyze the performance bottlenecks in GNN training and inference with GPUs empirically.
        % 
		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
        %
		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
        % 
		We decompose their running time and memory usage, evaluate the effects of hyper-parameters and assess the efficiency of the sampling techniques.
        %
		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
        %
        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has non-trivial overheads in sampling and data transferring.
	\end{abstract}

>>>>

	\begin{abstract}
		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
        %
		Recently, various graph neural network libraries have emerged.
        %
        They make the development of GNNs convenient, but their performance bottlenecks on large datasets are not well studied.
        %
		In this work, we analyze the performance bottlenecks in GNN training and inference with GPUs empirically.
        % 
		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
        %
		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
        % 
		We decompose their running time and memory usage, evaluate the effects of hyper-parameters and assess the efficiency of the sampling techniques.
        %
		The experimental evaluation with PyTorch Geometric indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
        %
        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has non-trivial overheads in sampling and data transferring.
	\end{abstract}
